Fragement size dependent pAU values (SIMULATION)
========================================================

Genomic fragments were simulated from a real-data 100kb alignment of all 8 taxa, that returns the assumed species tree. 
Seq-Gen simulated 100 replicates for sizes from 1000 to 100,000 bb with an increment of 1000bp given the species tree.  AU values were calculated with RAxML (GTRGAMMA model) and CONSEL.

Topologies are the same as for real-data AU test.

2015-20-29: Updated to new, more stringent, repeatmasked alignment.

```{r, echo=FALSE}
## Gives count, mean, standard deviation, standard error of the mean, and confidence interval (default 95%).
##   data: a data frame.
##   measurevar: the name of a column that contains the variable to be summariezed
##   groupvars: a vector containing names of columns that contain grouping variables
##   na.rm: a boolean that indicates whether to ignore NA's
##   conf.interval: the percent range of the confidence interval (default is 95%)
summarySE <- function(data=NULL, measurevar, groupvars=NULL, na.rm=FALSE,
                      conf.interval=.95, .drop=TRUE) {
    library(plyr)

    # New version of length which can handle NA's: if na.rm==T, don't count them
    length2 <- function (x, na.rm=FALSE) {
        if (na.rm) sum(!is.na(x))
        else       length(x)
    }

    # This does the summary. For each group's data frame, return a vector with
    # N, mean, and sd
    datac <- ddply(data, groupvars, .drop=.drop,
      .fun = function(xx, col) {
        c(N    = length2(xx[[col]], na.rm=na.rm),
          mean = mean   (xx[[col]], na.rm=na.rm),
          median = median   (xx[[col]], na.rm=na.rm),
          sd   = sd     (xx[[col]], na.rm=na.rm)
        )
      },
      measurevar
    )

    # Rename the "mean" column    
    datac <- rename(datac, c("mean" = measurevar))

    datac$se <- datac$sd / sqrt(datac$N)  # Calculate standard error of the mean

    # Confidence interval multiplier for standard error
    # Calculate t-statistic for confidence interval: 
    # e.g., if conf.interval is .95, use .975 (above/below), and use df=N-1
    ciMult <- qt(conf.interval/2 + .5, datac$N-1)
    datac$ci <- datac$se * ciMult

    return(datac)
}
```



# Load data 

```{r}
library(ggplot2)
library(grid)
setwd("/home/newuser/cephyr/data/2016-11-08/seqgen/")
df <-read.table("all_fragmens.fixed.pAU_values", sep="\t", header=TRUE)
df$tree <- NULL
colnames(df) <- c("id", "pAU", "frag_size")

df <- df[complete.cases(df),]
df <- subset(df, df$id %in% c("top1","top2","top3","top4","top5", "top6"))

df.s <- summarySE(df, measurevar="pAU", groupvars=c("frag_size","id"))

```

```{r}

# The palette with black:
cbPalette <- c("#000000", "#E69F00", "#56B4E9", "#009E73", "#0072B2", "#D55E00", "#CC79A7",  "#F0E442")

# To use for fills, add
#  scale_fill_manual(values=cbPalette)

# To use for line and point colors, add
#  scale_colour_manual(values=cbPalette)
```


When is significant rejection reached?
```{r}
head(subset(df.s, id == "top1" & pAU+ci > 0.95))
head(subset(df.s, id == "top2" & pAU+ci <= 0.05))
head(subset(df.s, id == "top3" & pAU+ci <= 0.05))
head(subset(df.s, id == "top4" & pAU+ci <= 0.05))
head(subset(df.s, id == "top5" & pAU+ci <= 0.05))

```

## Plot pAU over fragment_sizes

```{r, echo=FALSE, fig.width = 10, fig.height = 5}
p <- ggplot(df.s, aes(color=id, x=frag_size, y=pAU))
p + geom_line(size=1) + 
  ylim(-0.1,1.05) + 
  geom_errorbar(aes(ymin=pAU-ci, ymax=pAU+ci), width=.1) +
  geom_point() +
  #ggtitle("Size dependet AU values + CI") + 
  #geom_vline(xintercept=10000, color="darkgrey") + 
  geom_hline(aes(yintercept=.95), color="green") + 
  geom_hline(aes(yintercept=.05), color="red")  + 
  ylab("AU values") + 
  xlab("Fragment size") + 
  theme_classic() + 
  scale_colour_manual(values=cbPalette) + 
  scale_linetype_discrete(name  = "id",
                        breaks=levels(df.s$id),
                        labels=c("","Topology 1", "Topology 2", "Topology 3", "Topology 4", "Topology 5")) +
  theme(axis.text  = element_text(angle=0, vjust=0.5, size=12),
        legend.justification=c(1,0),
        legend.position=c(1,.4),
        legend.text = element_text(size=10, face="bold"),
        legend.title = element_blank()
        ) 

```


```{r, echo=FALSE, fig.width = 10, fig.height = 5}
df.s <- df.s[df.s$frag_size <=30000,]
p <- ggplot(df.s, aes(color=id, x=frag_size, y=pAU))
p + geom_line(size=1) + 
  ylim(-0.1,1.05) + 
  geom_errorbar(aes(ymin=pAU-ci, ymax=pAU+ci), width=.1) +
  geom_point() +
  #ggtitle("Size dependet AU values + CI") + 
  #geom_vline(xintercept=20000, color="darkgrey") + 
  geom_hline(aes(yintercept=.95), color="green") + 
  geom_hline(aes(yintercept=.05), color="red")  + 
  ylab("AU values") + 
  xlab("Fragment size") + 
  theme_classic() + 
  scale_colour_manual(values=cbPalette) + 
  scale_linetype_discrete(name  = "id",
                        breaks=levels(df.s$id),
                        labels=c("","Topology 1", "Topology 2", "Topology 3", "Topology 4", "Topology 5")) +
  theme(axis.text  = element_text(angle=0, vjust=0.5, size=12),
        legend.justification=c(1,0),
        legend.position=c(1,.4),
        legend.text = element_text(size=10, face="bold"),
        legend.title = element_blank()
        ) 

```


